### 2014-03-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update table structure in writeup

\bigskip 
\begin{minipage}{.8\linewidth}
\centering
\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
\begin{tabular}{c m{0.25in}}
\toprule[1.5pt]
Incident Time & Fire Behavior / Fireground Operation  \\
\midrule
17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
17:16    & Dispatch for a Still Alarm \\
17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
17:24    & Water applied to attic from the rear exterior position. \\
17:27    & IC calls a Mayday \\
17:29    & E123 Capt. carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\bigskip
\end{minipage}

@@

\bigskip
\begin{minipage}{.8\linewidth}
\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time           & 5 minutes                             & -- \\[.25cm]
 Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
                                   & $\rho$: 510 \; kg/m$^3$         & \\
                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
\bottomrule[1.25pt]
\end{tabular}\par
\bigskip
\end{minipage}

@@

\bigskip
\begin{minipage}{.8\linewidth}
\centering
\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
\begin{tabular}{ccccc}
\toprule[1.5pt]
Baseline Simulation & Alternative Simulation & Ventilation Area [m$^2$] & Type & Structure Side \\
\midrule
00    &  00   & 0.11 & Window      & Charlie \\
40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
45    &  45   & 0.12 & Breach      & Beta \\
55    &  55   & 0.12 & Breach      & Charlie \\     
130   &  N/A  & 1.41 & Door        & Charlie \\
135   &  N/A  & 0.2  & Breach      & Beta \\        
160   &  160  & 0.80 & Door        & Interior \\
300   &  300  & \multicolumn{3}{c}{Simulation Ends}  \\
\bottomrule[1.25pt]
\end{tabular}\par
\bigskip
\end{minipage}

>>>>

\begin{table}
\centering
\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
\begin{tabular}{l l}
\toprule[1.5pt]
Incident Time & Fire Behavior / Fireground Operation  \\
\midrule
\multirow{2}{*}{17:15} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
         & \\[.25cm]
17:16    & Dispatch for a Still Alarm. \\ [.25cm]
\multirow{2}{*}{17:20}    & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
         & \\[.25cm] 
17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
17:21:30 & 1$^{st}$ floor exterior porch door opened. \\[.25cm]
\multirow{2}{*}{17:23}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
         & \\[.25cm]
17:24    & Water applied to attic from the rear exterior position. \\[.25cm]
17:27    & IC calls a Mayday. \\[.25cm]
17:29    & E123 Capt. carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}
\centering
\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time           & 5 minutes                             & -- \\[.25cm]
 Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
                                   & $\rho$: 510 \; kg/m$^3$         & \\
                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

@@

\begin{table}
\centering
\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
\begin{tabular}{ccccc}
\toprule[1.5pt]
Baseline Simulation & Alternative Simulation & Ventilation Area [m$^2$] & Type & Structure Side \\
\midrule
00    &  00   & 0.11 & Window      & Charlie \\
40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
45    &  45   & 0.12 & Breach      & Beta \\
55    &  55   & 0.12 & Breach      & Charlie \\     
130   &  N/A  & 1.41 & Door        & Charlie \\
135   &  N/A  & 0.2  & Breach      & Beta \\        
160   &  160  & 0.80 & Door        & Interior \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
